Irt plot extra

### 2023-01-03 manuscript_v2.Rmd
Result section updated

An expert panel comprising all authors -- researchers from chronobiology, light research, neuroscience and psychology in different geographical contexts -- developed a comprehensive item pool of 48 items. The 48 items were examined independently based on their relevance and representativeness of the construct light-exposure related behaviour by each panel member, and modifications were suggested as required. The author team discussed the suggestions and amended the items as indicated, thus creating a 48-item inventory.

@@

Figures \@ref(fig:efagtPic1) and \@ref(fig:efagtPic2) summarise the response patterns of our total sample (n=`r nrow(sem.data)`) for all 48 items. Most of the items appeared skewed. The Shapiro–Wilk test of univariate normality [@shapiroAnalysisVarianceTest1965] and Mardia test of multivariate normality [@mardiaMeasuresMultivariateSkewness1970] indicated that our data violated both univariate and multivariate normality. The multivariate skewness was `r printnum(mardia.all.data$b1p)` (p \<0.001), and the multivariate kurtosis was `r printnum(mardia.all.data$b2p)` (p \<0.001).

>>>>

An expert panel comprising all authors -- researchers from chronobiology, light research, neuroscience and psychology in different geographical contexts -- developed a comprehensive item pool of 48 items. Face validity examination of all 48 items by each panel member indicated all items were relevant and appropriate and a few modifications were suggested as required. The author team discussed the suggestions and amended the items as indicated, thus creating a 48-item inventory.

@@

Figures \@ref(fig:efagtPic1) and \@ref(fig:efagtPic2) depict the response patterns of our total sample (n=`r nrow(sem.data)`) for all 48 items. Most of the items appeared skewed. The Shapiro–Wilk test of univariate normality [@shapiroAnalysisVarianceTest1965] and Mardia test of multivariate normality [@mardiaMeasuresMultivariateSkewness1970] indicated that our data violated both univariate and multivariate normality. The multivariate skewness was `r printnum(mardia.all.data$b1p)` (p \<0.001), and the multivariate kurtosis was `r printnum(mardia.all.data$b2p)` (p \<0.001).
